cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Add cone before cube in ordering

The `gen_expbranches(n, p, k)` function creates $k$ exponential branches in $2\text{-}D$, radiating from a central region (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:branch) a"} else { "Figure \\@ref(fig:branch-proj) a"})`). Each branch $i$ is defined as

>>>>

The `gen_expbranches(n, k)` function creates $k$ exponential branches in \gD{}, radiating from a central region. Each branch $i$ is defined as

### 2025-10-05 paper-cardinalR.tex
Add cone before cube in ordering

The \texttt{gen\_expbranches(n,\ p,\ k)} function creates \(k\) exponential branches in \(2\text{-}D\), radiating from a central region (Figure \ref{fig:branch-proj} a). Each branch \(i\) is defined as

>>>>

The \texttt{gen\_expbranches(n,\ k)} function creates \(k\) exponential branches in $2\text{-}D${}, radiating from a central region. Each branch \(i\) is defined as
